Old or Heavy?\\Decaying Gracefully with Age/Weight Shapes.

### 2019-03-02 papers/CADE19/paper.tex
converge figures for 10secs

\begin{table}[t]
\caption{Number of problems solved (top) and unique problems solved (bottom) by various configurations varying AWR, AWR shape, and AWR frequency.\label{tab:short:runs}}
\centering
\begin{tabular}{l|l|lllll|lllll}
&&  \multicolumn{5}{|c}{converge} &  \multicolumn{5}{|c}{decay} \\  
AWR & constant & \multicolumn{5}{|c|}{Frequency}  & \multicolumn{5}{|c}{Frequency} \\  
&& 1 & 10 & 100 & 1000 & Union & 1 & 10 & 100 & 1000 &Union  \\ \hline
\multicolumn{10}{c}{Problems Solved} \\ \hline
10:1		&5911 & 5908&5910 & 5969 &6135 &  & 5908 &5910  & 5969  &6135  \\
1:10		&6417& 6412&6421 &6389 & 6325  \\
1:100	&6026& 6028& 6010& 5971& 6148\\
1:1000	&5387&5395  &5408 &5510 &6019  \\ \hline
Union & \\ \hline \hline
\multicolumn{10}{c}{Uniquely Solved} \\ \hline
10:1		&1 & 4&2 & 5 &10 & 4&2 & 5&10 \\
1:10		& \\
1:100	& \\
1:1000	&\\ \hline
Union & \\ 
\end{tabular}
\end{table}

We ran Vampire in default mode (with {\tt discount} saturation algorithm) for 10s whilst varying  \texttt{age\_weight\_ratio} and \texttt{age\_weight\_ratio\_shape\_frequency} for both new values of \texttt{age\_weight\_ratio\_shape}. We also ran the constant default AWR of 1:1 as a baseline.

>>>>

\begin{table}[t]
\caption{Number of problems solved (top) and unique problems solved (bottom) by various configurations varying AWR, AWR shape, and AWR frequency.\label{tab:short:runs}}
\centering
\begin{tabular}{l|l|lllll|lllll}
	& & \multicolumn{5}{|c}{converge} & \multicolumn{5}{|c}{decay}\\  
AWR & constant & \multicolumn{5}{|c|}{Frequency} & \multicolumn{5}{|c}{Frequency}\\  
&& 1 & 10 & 100 & 1000 & Union & 1 & 10 & 100 & 1000 & Union\\
\hline
\multicolumn{10}{c}{Problems Solved} \\ \hline
10:1		& 7967 & 7972 & 7976 & 8050 & 8245 & 8372\\
1:10		& 8575 & 8565 & 8578 & 8550 & 8489 & 8778\\
1:100	        & 8079 & 8084 & 8079 & 8039 & 8279 & 8560\\
1:1000     	& 7276 & 7279 & 7297 & 7418 & 8133 & 8379\\
\hline
Union           & 9019 & 9028 & 9016 & 8981 & 8871 & 9194\\
\hline
\hline
\multicolumn{10}{c}{Uniquely Solved} \\ \hline
10:1		& 2 & 4 & 2 & 6 & 15 & 27\\
1:10		& 2 & 5 & 3 & 2 & 12 & 22\\
1:100	        & 1 & 2 & 2 & 9 & 13 & 26\\
1:1000	        & 1 & 2 & 0 & 0 & 5 & 7\\
\hline
Union           & 6 & 13 & 7 & 17 & 45 & --\\ 
\end{tabular}
\end{table}

We ran Vampire in default mode (with {\tt discount} saturation algorithm) for 10s whilst varying  \texttt{age\_weight\_ratio} and \texttt{age\_weight\_ratio\_shape\_frequency} for both new values of \texttt{age\_weight\_ratio\_shape}. We also ran the constant default AWR of 1:1 as a baseline. 
Experimental results for \emph{decay} were not complete at the time of submission but the trend is similar, e.g. some values performed better than others with a spread of unique results. These results will be added in a final version.
